Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2012-02-03 ms.tex
Updated figure 3 caption

\begin{figure*}
\begin{center}
\scalebox{0.75}{\plotone{f3.eps}}
\end{center}
\caption{Distribution of significances for Figure \ref{fig:skymaps} and a sampling radius of
$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean of -0.11 (close to zero) and
almost unit standard deviation.}
\label{fig:sigdist}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results} and
\ref{table:fermi}) for different integration radii (arrows with different grey scales), assuming
that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is adopted. These are
compared to integrated spectra of the same energy interval and aperture, assuming the universal
gamma-ray spectrum of clusters \citep[lines with different grey
scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic
interactions of CRs and ICM protons (dotted). For visualization purposes all photon fluxes are
weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.}
\label{fig:spectrum}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\scalebox{0.75}{\plotone{f3.eps}}
\end{center}
\caption{Distribution of significances for Figure \ref{fig:skymaps} and a sampling radius of
$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean $\mu=-0.11\pm 0.0059$ and
standard deviation $\sigma=1.01\pm 0.003$.}
\label{fig:sigdist}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral gamma-ray flux upper limits for \Fermi and VERITAS observations of the Coma
cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii
(arrows with different grey scales), assuming
that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is adopted. These are
compared to integrated spectra of the same energy interval and aperture, assuming the universal
gamma-ray spectrum of clusters \citep[lines with different grey
scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic
interactions of CRs and ICM protons (dotted). For visualization purposes all photon fluxes are
weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.}
\label{fig:spectrum}
\end{figure*}
